Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-15 Paper/paper.tex
Have fixed slight error in proof (still need to refactor proof completely)

Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $U_{NH}(k^*)=t$ and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}

>>>>

Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}
